---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
The following code is used to test hypothesis related to the relationship between a country's forest area, level of CO2 emissions and the employment rate. 


We will be calling an excel file from Github and reading it into R. For R to read the excel file we call-up the 'rio' package from the R Library. After reading in the data frame, we name it TM2_Data. 
```{r}
library(rio)
#install_formats()
linkexcel='https://github.com/PUBPOL542G3/G3_Merge/blob/main/Triple_Merge.xlsx?raw=true'
TM2_Data=import(linkexcel)
```

This code resets the indexes of TM2_Data to match the "R" format indexes. 
```{r}
row.names(TM2_Data)=NULL
```

Using the code below, we verify the data structure including the characteristics of each variable. The output from the code shows that our data has two character variables and three numeric variables.
```{r}
str(TM2_Data,width = 50,strict.width='cut')
```

Here we state our hypotheses as the following: 
Hypothesis 1: we expect forest area to increase as CO2 decreases
Hypothesis 2: we expect forest area to increase as employment & CO2 decrease
The second hypothesis examines the interaction between employment and CO2.
The regression for the second hypothesis takes on the form: forest area = constant + a_CO2 + b_employment + c_CO2*employment
```{r}
hypo1=formula(forest_area~ CO2)
hypo2=formula(forest_area~ employment*CO2)
```



The code below computes the two gaussian regression models for the hypotheses listed above.
```{r}
gauss1=glm(hypo1,
           data = TM2_Data,
           family = 'gaussian')

gauss2=glm(hypo2,
           data = TM2_Data,
           family = 'gaussian')
```

This code displays the results of the first gaussian regression model created in the above code. This regression model shows no significant correlation (at the 5% level of significance) between our independent and dependent variables (CO2 and forest area respectively) listed in hypothesis 1. 
```{r}
summary(gauss1)
```

This code displays the results of the second gaussian regression model created above. This regression model shows no significant correlation (at the 5% level of significance) between our independent variables, their interaction effect, and the dependent variable listed in hypothesis 2. 
#displaying the results from regressional model 2
```{r}
summary(gauss2)
```

This code uses the anova function to search for the better of our two regression models (i.e. hypothesis 1 and hypothesis 2). After running the function, neither model seemed very promising. 
```{r}
anova(gauss1,gauss2,test="Chisq")
```

This code calls up the RSquared packages from the R library. We use this function to view the R squared value of our second gaussian model. The function revealed a very low RSquared value which means that out model only explains 1% of the variance in our data. 
```{r}
library(rsq)
rsq(gauss2,adj=T)
```

We can also create a dotwhisker plot in order to see the variance in our data. To do this we call on the dotwhisker package from the library.
```{r}
#install.packages("dotwhisker")
library(dotwhisker)
```

The dwplot command displays our three variables in dotwhisker plot form. These plots show that our employment data has very long 'whiskers' representing a wide range of data points. 
```{r}
dwplot(gauss2,by_2sd = F)
```

This code calls up the margins package from the R library. With margins we create another data visualization that depicts the marginal effects of the CO2 variable in the model.
```{r}
library(margins)
cplot(gauss2,'CO2')
```


We repeat the same command as above, however, this time we are using the employment variable in the model. 
```{r}
cplot(gauss2,'employment')
```

Using the persp function, we are also able to plot the interaction effect between CO2 and employment.  
```{r}
persp(gauss2)
```







